---
title: "RR_week2"
date: "01/06/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mice)
library(ggplot2)
library(dplyr)
library(tidyr)

data<- read.csv("activity.csv")
```

## Course Project 1  


# What is mean total number of steps taken per day?


total number of steps taken per day
```{r}

x<- sum(data$steps, na.rm = TRUE)
x
```

```{r}

data_day<- data%>%
  group_by(date)%>%
  summarise(sum_steps = sum(steps, na.rm = T))
data_day$sum_steps<- as.numeric(data_day$sum_steps)
                              
ggplot(data_day, aes(x = sum_steps )) + geom_histogram( fill = 'steel blue')
```

mean and median of the total number of steps taken per day
```{r}

data%>%
  summarize(median = median(steps, na.rm = T), mean = mean(steps, na.rm = T))
```
# What is the average daily activity pattern?

```{r}

data$date <- as.Date(data$date, format= "%Y-%m-%d")

```

```{r}
data2<- data%>%
  group_by(interval)%>%
  summarise(avg = mean(steps, na.rm = T))

ggplot(data2, aes(interval, avg))+geom_line()


```
5 minute interval who contains the maximum number of steps
```{r}

data2%>%
  slice(which.max(avg))
```
# Imputing missing values
sum of missing data
```{r}
sum(!complete.cases(data))
```
Filling the missing data thanks to the mice package.

```{r}
act<- data.frame(data)
temp<- mice(act, m=5, method = "pmm", seed = 509)
completed<- complete(temp, 1)
 
```

histogram with the completed dataset.
```{r}
comp<- data.frame(completed)
completed2<- completed%>%
  group_by(date)%>%
  summarise(sum_step =  sum(steps))
ggplot(data = completed2, aes( x = sum_step))+geom_histogram()

```
calculation of mean and median
```{r}
completed2%>%
  summarise(mean= mean(sum_step), median = median(sum_step))
```
the mean and the median are now way higher than before. 

#differences in activity patterns between weekdays and weekends

```{r}
#create new column with the different day of the week
completed<- completed%>%
  mutate(days = weekdays(date))

#create another column and put either week day or week end depending on the day. 

completed<- completed%>%
  mutate(week_end = if_else(days == c("lundi","mardi","mercredi","jeudi","vendredi"), "week_day", "week_end"))
```

plot

```{r}
plot<- completed%>%
  group_by(interval, week_end)%>%
  summarise(avg = mean(steps, na.rm = T))

ggplot(plot, aes(interval, avg))+geom_line()+facet_wrap("week_end")
```

